---
title: "Dynamic QMD blocks"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Dynamic QMD blocks}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

`knitBlock()` composes reusable QMD fragments at render time. It reads a QMD
block, expands Quarto include shortcodes, rewrites labels with a caller-supplied
stem, evaluates the block with caller-supplied variables, and emits markdown
through `knitr::knit_child()`.

The helper belongs to NGR because QMD chunks call it inside the R/knitr runtime.
The `qrt` CLI still owns render execution; it should not silently inject this R
helper into documents.

## Mother Blocks And Child Views

Use the default `labels = "parent"` for reportable mother blocks. In this mode,
labels in the requested block are rewritten with `stem`, while labels and
captions in recursively included child blocks are stripped. This keeps one
figure or table number for the reportable object and avoids numbering every
internal tab or view.

Use `labels = "strip"` when the whole block is an internal view that should not
create figure or table numbers. Use `labels = "rewrite"` only when every label
in the expanded include tree is intended to remain numbered.

## Minimal Example

```{r example}
library(NGR)

Root <- file.path(tempdir(), "ngr-knit-block-vignette")
unlink(Root, recursive = TRUE, force = TRUE)
dir.create(file.path(Root, "_tbl"), recursive = TRUE)

writeLines(c(
  "```{r}",
  "#| label: tbl-site-view",
  "#| tbl-cap: \"Internal site/model view\"",
  "knitr::kable(data.frame(site = siteID_TARGET, model = ID_TARGET))",
  "```"
), file.path(Root, "_tbl", "site.qmd"))

writeLines(c(
  "{{< include /_tbl/site.qmd >}}",
  "",
  "```{r}",
  "#| label: tbl-hazard-summary",
  "#| tbl-cap: !expr CAP",
  "knitr::kable(data.frame(site = siteID_TARGET, model = ID_TARGET, value = VALUE))",
  "```"
), file.path(Root, "_tbl", "hazard.qmd"))
```

The same mother block can now be called repeatedly with different stems and
different render context:

```{r repeated-calls, results = "asis"}
knitBlock(
  path = "/_tbl/hazard.qmd",
  stem = "site-a-model-1",
  vars = list(
    siteID_TARGET = "SITE_A",
    ID_TARGET = "MODEL_1",
    VALUE = 0.42,
    CAP = "Hazard summary for SITE_A / MODEL_1."
  ),
  root = Root
)

knitBlock(
  path = "/_tbl/hazard.qmd",
  stem = "site-b-model-2",
  vars = list(
    siteID_TARGET = "SITE_B",
    ID_TARGET = "MODEL_2",
    VALUE = 0.67,
    CAP = "Hazard summary for SITE_B / MODEL_2."
  ),
  root = Root
)
```

## Contract

`stem` must be unique for every numbered call in one render. If the same dynamic
label is emitted twice, `knitBlock()` fails explicitly instead of allowing an
ambiguous Quarto cross-reference.

`vars` is a named list. It is the place to pass selectors and captions that the
QMD fragment already understands, such as `ID_TARGET`, `siteID_TARGET`,
`TR_TARGET`, `CAP`, or project-specific equivalents. `knitBlock()` does not know
about PSHA, sites, models, or captions.

## Direct Helper Or Project Scaffold

Use `knitBlock()` directly in a QMD `results: asis` chunk when a report or
presentation needs to repeat a shared block for several sites, models, or
language-specific captions.

Project scaffolds can provide higher-level loops, but they should still leave
scientific calculations and data production to their producer libraries. NGR
only owns QMD include expansion, label rewrite/strip/check behavior, and
`knitr::knit_child()` execution.
