---
title: "buildPlot line and point layers"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{buildPlot line and point layers}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", eval = FALSE)
```

`buildPlot()` composes highcharter plots from table-like inputs. The common
pattern is one `data.table` for line series and, when needed, a second
`data.table` for point series. Both tables use `ID` to define the series and
`X`/`Y` for coordinates.

## Line And Point Inputs

Line data can include optional style columns such as `style` and `fill`. Point
data can include marker style columns.

```{r line-point-data}
library(NGR)
library(data.table)

DataLines <- data.table(
  ID = rep(c("A", "B", "C"), each = 5),
  X = as.numeric(rep(1:5, 3)),
  Y = as.numeric(c(seq(1, 5), seq(2, 6), seq(3, 7))),
  style = c(rep("solid", 5), rep("dotted", 5), rep("dashed", 5)),
  fill = c(rep(TRUE, 5), rep(TRUE, 5), rep(FALSE, 5))
)

DataPoints <- data.table(
  ID = rep(c("A", "B", "C"), each = 4),
  X = as.numeric(rep(1:4, 3)),
  Y = as.numeric(c(seq(8, 11), seq(6, 9), seq(4, 7))),
  style = c(rep("circle", 4), rep("diamond", 4), rep("triangle-down", 4))
)
```

## Combined Plot

Pass line and point layers together. `line.type = "spline"` uses curved line
segments while preserving the point layer.

```{r combined-plot}
PLOT <- buildPlot(
  data.lines = DataLines,
  data.points = DataPoints,
  line.type = "spline",
  plot.title = "Combined Lines and Points Example",
  plot.subtitle = "Demonstration of fills, line styles, and point styles",
  plot.height = 500,
  plot.width = 700,
  xAxis.legend = "Time (units)",
  yAxis.legend = "Value",
  print.max.abs = FALSE
)

PLOT
```

## Required Columns

For line series:

| Column | Role |
|---|---|
| `ID` | series identifier |
| `X` | x coordinate |
| `Y` | y coordinate |

For point series, the same `ID`, `X`, and `Y` columns are required. Optional
columns such as `style`, `size`, `fill`, or `yAxis` are consumed when present
by the plotting helper.

## Related Articles

Use the secondary-axis article when the plot needs a linked or independent
right-hand axis. Use the gridline-theme article when plotting on log axes.
