---
title: "Quarto YAML Helpers"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quarto YAML Helpers}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

# Purpose

NGR provides small Quarto/YAML helpers for R code that needs qrt-style runtime
configuration without shelling out to the `qrt` CLI.

The `qrt` runtime scripts remain CLI adapters. These functions are the reusable
R API.

# Build A Runtime Book Config

```{r}
library(NGR)

work <- file.path(tempdir(), "ngr-quarto-yaml-vignette")
unlink(work, recursive = TRUE, force = TRUE)
dir.create(file.path(work, "yml"), recursive = TRUE)
dir.create(file.path(work, "_chapters"), recursive = TRUE)
dir.create(file.path(work, "bib"), recursive = TRUE)

manifest_path <- file.path(work, "report.qmd")
base_path <- file.path(work, "yml", "_quarto.yml")

writeLines(c(
  "---",
  "title: Example Report",
  "chapters:",
  "  - _chapters/intro.qmd",
  "bibliography: bib/references.bib",
  "---",
  "",
  "# Body"
), manifest_path)

writeLines(c(
  "project:",
  "  type: default",
  "  preview: false",
  "execute:",
  "  echo: true",
  "format:",
  "  html:",
  "    toc: true"
), base_path)

frontmatter <- quartoReadFrontmatter(manifest_path)
base <- yaml::read_yaml(base_path)
book_config <- quartoMergeBookManifest(base, frontmatter)

cat(quartoAsYaml(book_config))
```

The single chapter remains a YAML sequence, and logical values are emitted as
`true`/`false` for Quarto compatibility.

# Single File Render Scope

```{r}
single_file_config <- quartoSetProjectRender(base, "report.qmd")
cat(quartoAsYaml(single_file_config))
```

# DOCX Book Profile

```{r}
docx_profile <- list(format = list(docx = list(toc = TRUE, `number-sections` = FALSE)))
docx_book_profile <- quartoDocxBookProfile(docx_profile)
cat(quartoAsYaml(docx_book_profile))
```

